# Conclusion

Golden Cross Investment Return:

Componded Return calculated in Excel (INDIRECT(ADDRESS(ROW()-1,COLUMN())) * (1 + T2)), assuming an initial investment of $10000

```{r, include=FALSE}
aapl_gain = read.csv(file = 'aapl_gain.csv')
cost_gain = read.csv(file = 'cost_gain.csv')
msft_gain = read.csv(file = 'msft_gain.csv')
tsla_gain = read.csv(file = 'tsla_gain.csv')
nvda_gain = read.csv(file = 'nvda_gain.csv')
gm_gain = read.csv(file = 'gm_gain.csv')

```


```{r, include=FALSE}
aapl_gain$sym <- 'aapl'
cost_gain$sym <- 'cost'
msft_gain$sym <- 'msft'
tsla_gain$sym <- 'tsla'
nvda_gain$sym <- 'nvda'
gm_gain$sym <- 'gm'
```


```{r, include=FALSE}
df_stock <- rbind(aapl_gain, cost_gain ,msft_gain, tsla_gain,nvda_gain,gm_gain )
```


```{r}
ggplot(df_stock, aes(x=Date, y=X10000, group=sym, color = sym))+
  geom_line(aes(group=sym))+
  geom_point() +
  xlab('Trading Days')+
  ylab('Investment Returns ($)')+
  labs(title="Golden Cross Investment Returns Over time (Start from $10000)")
```

```{r}
ggplot(df_stock, aes(x=reorder(sym,growth, median, na.rm = TRUE), y=growth, color=sym)) + 
  geom_boxplot() + coord_flip() +
  xlab('Stock')+
  ylab('Investment Growth Over Time')+
  labs(title="Golden Cross Investment Returns Over time")
```

```{r}
compond_rate = c(tail(aapl_gain$rate, n=1),
                 tail(cost_gain$rate, n=1),
                 tail(msft_gain$rate, n=1),
                 tail(tsla_gain$rate, n=1),
                 tail(nvda_gain$rate, n=1),
                 tail(gm_gain$rate, n=1))

df_compond <- data.frame(compond_rate)

ggplot(df_compond, aes(y= df_compond$compond_rate)) + 
  geom_boxplot()+
  geom_hline(yintercept=0.8294, linetype="dashed", color = "red", size=1)+
  annotate(geom="text", x=0, y=-1, label="82.94% average S&P 500 return from 2019 to 2021",
              color="red")+
  ylab('Investment Compond Growth rate')+
  labs(title="Golden Cross Investment Compond Return Rate (All the stock combined)")

```
```{r}
df_compond$compond_rate
```
The data of the actual return of S&P 500 over years comes from Webull Stock Broker.

The Golden Cross scheme managed to achieve a median return much higher than the average return of S&P 500 Index funds over the span of the data (Two years). This investment plan outperform the general market when being applied to major stocks that are included in the index funds.
