--- 
title: "Golden Cross"
author: "Vipul H Harihar, Zhaoyu Wu, Zhirui Yang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# Introduction

EDAV Final Project Assignment: Golden Cross

## Final Project Group: Vipul Harihar, Zhaoyu Wu and Zhirui Yang Introduction

The world is changing and adapting to cope with the major technological advancements and changes but we never realized that ‘Data’, the term that used to describe statistics, would be so huge by the first quarter of the 21st Century. Superficially from a bird's eye view we may say small governments, corporations, and individuals focus more on human impact to the environment while international financial markets have responded with innovative products to help manage climate risk and invest in mitigating technologies. Big firms play a key function in markets, committing capital to bridge timing differences between buyers and sellers. With the financial industry debating underlying market structure tenets such as tick sizes there has been renewed focus on different types of market making activity.

## Why ‘Stocks’ ? What is ‘Stock Exchange’? 
A stock or the term share is usually used in representing a company's equity. We may understand it as a financial instrument that assists in showing ownership in a corporation or a company and it represents a proportionate claim on its assets (what it owns) and earnings (what it generates in profits). When we think of the term share stock exchanges, it is the secondary market, where existing owners of shares can transact these shares of their equities with potential buyers. It is important to comprehend that the corporations on stock markets do not buy and sell their own shares on a regular basis (companies may engage in stock buybacks or issue new shares, but these are not day-to-day operations and often occur outside of the framework of an exchange). So we may sum it as whenever you buy a share of stock on the stock market, you are not buying the stock directly from the company, you are buying it from another existing shareholder. Likewise, when you want to sell the shares you own , they are not sold to the company—rather you sell them to some other investors.

Project Problem Statement There are numerous people in the market who want to invest in the stock market are way too afraid to put their life’s savings at stake. Many people pour their life savings and dump their 401K (contribution retirement plan) into the stock and option market. They perform various strategies and financial maneuvers, hoping to gain massive profits but generally end up losing most of their investments or still having underperformance in the general market. Thus, our team started thinking if there is an investing strategy that can consistently beat the index fund return.

EDAV Final Project Assignment

A recently published article by Barclays on Impact of Retail Options Trading (https://www.docdroid.net/5gM68EW/barclays-us-equity-derivatives-strategy-impact-of-retailoptions-trading-pdf) raised an interesting theory: the market participation of the retail traders (the ordinary traders like us) creates a systematic dislocation between the implied volatility and the actual price volatility of stocks. The article also claims that there are two possible ways to generate profits from this dislocation: • Hedged straddle • Call spreads

##  What Does a Golden Cross Tell You?

There are three stages to a golden cross. In the second stage, the shorter moving average forms a crossover up through the larger moving average to trigger a breakout and confirmation of trend reversal. The moving averages act as support levels on pullbacks until they crossover back down at which point a death cross may form. The death cross is the opposite of the golden cross as the shorter moving average forms a crossover down through the longer moving average.

With a bellwether index, the motto «A rising tide lifts all boats» applies when a golden cross forms as the buying resonates throughout the index components and sectors. Day traders commonly use smaller time periods like the 5-period and 15-period moving averages to trade intra-day golden cross breakouts. The larger the chart time frame, the stronger and lasting the golden cross breakout tends to be.

The Difference Between a Golden Cross and a Death Cross

A golden cross indicates a long-term bull market going forward, while a death cross signals a long-term bear market. The golden cross occurs when a short-term moving average crosses over a major long-term moving average to the upside and is interpreted by analysts and traders as signaling a definitive upward turn in a market.

Limitations of Using the Golden Cross

Many times, an observed golden cross produces a false signal. Despite its apparent predictive power in forecasting prior large bull markets, golden crosses also do regularly fail to manifest. Therefore, a golden cross should always be confirmed with other signals and indicators before putting on a trade.

What Does a Golden Cross Indicate?

A golden cross suggests a long-term bull market going forward.

Are Golden Crosses Reliable Indicators?

Traders often use a golden cross as confirmation of a trend or signal in combination with other indicators.

How are we going to Proceed?

Data Sources- data has to be historical
Data Collection from valid resources
Using Accurate metrics to define our problem questions
Plotting exploratory data analytics visuals, including CAGR (componded annual growth rate) and bootstrap simulation
Using d3.js / plotly.js for better understanding and deeper insights (if time permits)
Summary: What are we going to do in the primary phase of the project? 
• A financial study on the stock market published last year raised an intriguing theory 
• Golden Cross and it’s capabilities EDAV Final Project Assignment 4 
• Data Cleaning and Exploration
• Report writing and visuals finalization 
• Study on the paper published by Barclay Equity Research: Impact of Retail Options Trading

## Current Questions under study: We are primarily focusing on these questions mentioned below:

Data Investigation and checking if ‘olden Cross’ exists by analyzing the trends in the past 10 years data?
Examination from a pure data perspective, using the visualization techniques to demonstrate the difference between the implied volatility and historical volatility.
What are some of the factors that influence the magnitude of this dislocation?
Do spread calls and hedged straddles effectively monetize this dislocation and consistently beat the general market return? (Bootstrap stimulation)
Calculation of the golden cross Data Source and its availability: We have a variety of data sources available to us. But as we are aware of this data being so valuable we couldn’t get it for free thus on digging up deep, we found the Yahoo Finance Website. (The Yahoo! Finance is a media property that is part of the Yahoo! network. It provides financial news, data and commentary including stock quotes, press releases, financial reports, and original content. It also offers some online tools for personal finance management.) We are going to work and cover the industrial giants in the stock market and provide and collate actual and relevant data sources from the Yahoo finance website, itself. 

Actual price data: https://finance.yahoo.com/ Stock lists: (Index ETF: S&P 500) • Alphabet Inc. :https://finance.yahoo.com/quote/GOOG?p=GOOG&.tsrc=fin-srch • Apple: https://finance.yahoo.com/quote/AAPL?p=AAPL&.tsrc=fin-srch • Tesla: https://finance.yahoo.com/quote/TSLA?p=TSLA&.tsrc=fin-srch • Walmart: https://finance.yahoo.com/quote/WMT?p=WMT&.tsrc=fin-srch • Wells Fargo & Company: https://finance.yahoo.com/quote/WFC?p=WFC&.tsrc=fin-srch • Paypal Holdings & Inc: https://finance.yahoo.com/quote/PYPL?p=PYPL&.tsrc=fin-srch • JPM & Chase: https://finance.yahoo.com/quote/JPM?p=JPM&.tsrc=fin-srch • McDonald: https://finance.yahoo.com/quote/MCD?p=MCD&.tsrc=fin-srch • PepsiCo: https://finance.yahoo.com/quote/PEP?p=PEP&.tsrc=fin-srch

EDAV Final Project Assignment Footnotes Sample Data Set (Just for introductory purpose) Open: The starting period of trading on a securities exchange or organized over-the-counter market High: The high is the highest price at which a stock traded during a period. Low: The low is the lowest price of the period. Close: The close is a reference to the end of a trading session in the financial markets when the markets close for the day. Adj Close: The adjusted closing price amends a stock's closing price to reflect that stock's value after accounting for any corporate actions. Volume: Is the measure of how much of a given financial asset has traded in a period of time. Resources: https://www.docdroid.net/5gM68EW/barclays-us-equity-derivatives-strategy-impact-of-retailoptions-trading-pdf https://www.investopedia.com/articles/investing/082614/how-stock-market-works.asp https://www.investopedia.com/terms/i/iv.asp

<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data sources


<!--chapter:end:02-data.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data transformation

## Load packages

Please click this link to see our work more precisely. Thank you :)
https://github.com/Alex2Yang97/GoldenCross_5702final


<!--chapter:end:03-cleaning.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Missing values

```{r}
knitr::opts_chunk$set(fig.width=8, fig.height=12)
```

```{r}
library(fivethirtyeight)
library(tidyverse)
library(patchwork)
library(plotly)
```


=======
As what we mentioned in Final Project Data Check, we are working on the financial data, like the open and close prices of stocks. All these data are publicly available, so there is no missing values. Although we can regard non-trading days as missing value, in fact these missing values don’t matter at all because all public marketing behaviors stop at these days. Moreover, we are calculating some technical indicators, like moving average with different time span, so there will be some missing values (Null value) at the beginning of the data because there is not enough data to calculate the sliding window. However, in our trading strategies, we need to drop all Null values at the beginning of our backtesting intervals in order to get accurate technical indicators. Therefore, in this way we don’t have any missing value in our raw data and processed data. We will use "backup" data for this missing value chapter. In this chapter, we will use avengers Dataset.



## Basics of avengers Dataset

The first step is to load data and check the basic information about the data. We should know the dimension of the dataset and the meaning of each column.


```{r}
head(avengers)
```

```{r}
colnames(avengers)
```

```{r}
dim(avengers)
```


## Check Missing Values

We will check the missing values in the whole data.

```{r}
colSums(is.na(avengers)) %>%
  sort(decreasing = TRUE)

rowSums(is.na(avengers)) %>%
  sort(decreasing = TRUE)
```

We can see that there are lots of missing values in the data. To better understand there distribution, we will transfer the missing value into a binary variable "missing", then plot a heatmap to show the missing value.

```{r}
avengers_nan <- avengers %>% 
    rownames_to_column("id") %>% 
    gather(key, value, -id) %>% 
    mutate(missing = ifelse(is.na(value), "yes", "no")) 
avengers_nan
```


```{r fig.width=5, fig.height=20}
ggplot(avengers_nan, aes(x = key, y = fct_rev(id), fill = missing)) +
  geom_tile(color = "white") + 
  ggtitle("Missing value in data") +
  scale_fill_viridis_d() + # discrete scale
  theme_bw() +
  theme(legend.position = 'None', axis.text.x = element_text(angle = 60, hjust = 1))
```

We can find that most of missing values appeared in the "death" or "return" columns. These columns represent the number of deaths and returns of characters. In Marvels, it is very common for some superheroes or super devils to resurge many times. Therefore, we can estimate that these missing values may represent the importance or the power of characters. For example, some important or powerful characters may seldom die or could resurge every time they die.

Therefore, we select all the "death" columns and plot the heatmap.

```{r}
death <- avengers[, c('name_alias', 'death1', 'death2', 'death3', 'death4', 'death5')]
death_nan <- death %>% 
    gather(key, value, -name_alias) %>% 
    mutate(missing = ifelse(is.na(value), "yes", "no")) 
head(death_nan)
```


```{r fig.width=5, fig.height=20}
ggplot(death_nan, aes(x = key, y = fct_rev(name_alias), fill = missing)) +
  geom_tile(color = "white") + 
  ggtitle("Missing value in death") +
  scale_fill_viridis_d() +
  theme_bw() +
  theme(legend.position = 'None', axis.text.x = element_text(angle = 60, hjust = 1))
```

All the rows (characters) have "True" value in "death1" columns. It means that every character has at least one death, which may represent all the superpowers were born of fire. This is actually how the Marvels start a superhero story. Superhero typically got superpowers by some disasters or accidents at the beginning of the story.

Then we can check two famous superheroes, Iron man and Jocasta.

```{r}
death %>% filter(name_alias=='Anthony Edward "Tony" Stark')
```

```{r}
death %>% filter(name_alias=='Jocasta')
```

We can see that Tony only died once. In Marvels, Iron man is one of the most power superhero, and he fight many times successfully.\n He only died in the fighting with Thanos. He is also the most important in Marvels movies. And Jocasta is a "non-living" construct.\n She did not has strong power, but she could resurge because she required no food, water, or oxygen to survive and she was also \n immune to poisons and diseases. She is also one of the most important character of Marvels cartoons. It fits our initial hypothesis\n for the number of daeth.\n

Then we can also show the heatmap of "return" columns.\n

```{r}
return <- avengers[, c('name_alias', 'return1', 'return2', 'return3', 'return4', 'return5')]
return_nan <- return %>% 
    gather(key, value, -name_alias) %>% 
    mutate(missing = ifelse(is.na(value), "yes", "no")) 
head(return_nan)
```

```{r fig.width=5, fig.height=20}
ggplot(return_nan, aes(x = key, y = fct_rev(name_alias), fill = missing)) +
  geom_tile(color = "white") + 
  ggtitle("mtcars with NAs added") +
  scale_fill_viridis_d() +
  theme_bw() +
  theme(legend.position = 'None', axis.text.x = element_text(angle = 60, hjust = 1))
```

## Check missing values by year

We will check missing values by year. We can find if there is a pattern of the number of death or return.

There are the years when the Marvels had a new character. We can see that there are some big gaps between certain years. From these years we can know the productive periods of Marvels.

```{r}
unique(avengers$year) %>%
  sort(decreasing = FALSE)
```

We gather all "death" columns into one "death" columns.

```{r}
death <- avengers[, c('year', 'death1', 'death2', 'death3', 'death4', 'death5')]
death_nan <- death %>% 
    gather(key, death, -year)
death_nan <- subset(death_nan, select = -c(key))
head(death_nan)
```

```{r}
# https://stackoverflow.com/questions/26017640/using-dplyr-summarise-each-with-is-na
death_perc <- death_nan %>% 
  group_by(year) %>%
  summarise_each(funs(sum(is.na(.)) / length(.)))
```

```{r}
characters_num <- aggregate(death ~ year, data = death_nan, FUN = length)
characters_num
```

```{r}
fig <- plot_ly(
  death_perc,
  x = ~year,
  y = ~death,
  type = "bar"
)
fig <- fig %>% layout(title = "The persentage of Missing values in Death",
         xaxis = list(title = "The persentage of Missing values"),
         yaxis = list(title = "Year"))
fig
```

```{r}
fig <- plot_ly(
  characters_num,
  x = ~year,
  y = ~death,
  type = "bar"
)

fig <- fig %>% layout(title = "The number of Missing values in Death",
         xaxis = list(title = "The number of Missing values"),
         yaxis = list(title = "Year"))

fig
```

We count the number of characters and the percentage of missing values for each year. We can see that although the number of characters differ greatly each year, the percentage of missing values is pretty stable each year. It means that Marvels will keep certain proportion of character to be alive.

## Using function from Q2 of Pset4

```{r}
#Creation of the Function 
missing_plot_function <- function(data, per = FALSE){
     missing_patterns <- data.frame(is.na(data)) %>%
     group_by_all() %>%
     count(name = "count", sort = TRUE) %>%
     ungroup()

  # Sorting the missing patterns in Decreasing
  missing_patterns <- missing_patterns[order(missing_patterns$count, decreasing = TRUE), ]
  
  # Storing the sorted colnames in the variable sorted_colnames
  sorted_colnames <- colSums(is.na(data)) %>% 
  sort(decreasing = TRUE)
  
  # Sorting again keeping the sorted colnames under consideration
  missing_patterns <- missing_patterns[, append(names(sorted_colnames), "count")]
        row_number <- which(!apply(as.data.frame(missing_patterns)[1:dim(missing_patterns)[2]-1], 1, any))
  
  # Rownames columns will serve as y-axis
  missing_patterns$rownames <- row.names(missing_patterns)
  
  # tidydata for plotting
  tidy_data <- missing_patterns %>%
               select(-count) %>% 
               pivot_longer( -rownames, names_to = "Names", values_to = "Missing") 
  
  # Plot the core missing value plot
  center_part <- tidy_data %>% 
                 ggplot(aes(x = factor(Names, levels = names(sorted_colnames)),
                 y = fct_rev(factor(rownames, levels = missing_patterns$rownames)),
                 fill = Missing)) +
                 geom_tile(color = "white", show.legend = FALSE) +
                 annotate("text", x = dim(data)[2] %/% 2,y = nrow(missing_patterns) - row_number + 1,
                     label = "Complete Cases") +
                     scale_fill_brewer(palette = "BuPu") +
                     xlab("Variable") +
                     ylab("Missing Pattern")+
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
  
  # Plot the missing values of a column
  top_df_part <- data.frame(as.list(sorted_colnames)) %>% 
                 pivot_longer(everything(),names_to = "Names",values_to = "num_rows_missing")
  
  if (per) { top_df_part$num_rows_missing = top_df_part$num_rows_missing*100/nrow(data)}
    
  top_part <- top_df_part %>% 
    ggplot(aes(x = factor(Names, levels = names(sorted_colnames)),
               y = num_rows_missing)) +
    geom_bar(stat = "identity",  fill = "steelblue", alpha=0.5) +
    xlab("Variable") +
    ylab(ifelse(per, "% Rows Missing", "Num Rows\n Missing"))+
     theme(axis.title.x =element_blank(),
           panel.grid.major.x = element_blank(),
           panel.grid.minor.x = element_blank(),
           axis.text.x = element_text(angle = 60, hjust = 1))
      
  
  # plot the row count for patterns
  right_df_part <- missing_patterns
  
  if (per) {
    right_df_part$count = right_df_part$count*100/nrow(data)
  }
    
  right_part <- right_df_part %>% 
    ggplot(aes(x = fct_rev(factor(rownames, levels = missing_patterns$rownames)),
               y = count)) +
    geom_bar(stat = "identity",  fill = "steelblue", alpha=0.5) +
    coord_flip() +
    xlab("Variable") +
    ylab(ifelse(per, "% Rows", "Row Count"))+
     theme(axis.title.y =element_blank(),
           panel.grid.major.y = element_blank(),
           panel.grid.minor.y = element_blank(),
           axis.text.x = element_text(angle = 60, hjust = 1))
      
  
  design <- "
    1#
    23
  "
  
  top_part + center_part + right_part + plot_layout(design = design, widths = c(3,1), heights = c(1,3))
}
```



```{r fig.width=15, fig.height=9}
missing_plot_function(avengers, per = FALSE)
```



```{r fig.width=15, fig.height=9}
missing_plot_function(avengers, per = TRUE)
```


We can see the distribution of missing values by using the function. The result is pretty similar to what we did above. There are only few columns is totally complete and most of missing values are concentrated in "death" and "return" columns. Meanwhile, there is no missing values in some columns including "current", "year", "gender".
<<<<<<< HEAD
>>>>>>> Stashed changes
>>>>>>> 07b14f4bcc72b559dff4a997ba31f1f64cde01c1
=======
>>>>>>> 2b7893f12026372d5019bd7e224f9ffdc53594bc

<!--chapter:end:04-missing.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Results

The following packages are needed for the visualization: 

```{r}
library(plotly)
library(quantmod)
library(ggplot2)
library(dplyr)
library(TTR)
library(vcd)
library(ggridges)

```


The price data would be acquired from yahoo finance using quantmod package

```{r, include=FALSE}


symbolBasket <- c('AAPL', 'GM', 'TSLA', 'MSFT', 'NVDA', 'COST')
getSymbols(symbolBasket , src='yahoo')

```


```{r, include=FALSE}
AAPL1 <- as.xts(`AAPL`)
names(AAPL) <- c("AAPL.Open"   ,  "AAPL.High"   ,  "AAPL.Low"   ,   "AAPL.Close"  ,  "AAPL.Volume", "AAPL.Adjusted")

GM1 <- as.xts(`GM`)
names(GM) <- c("GM.Open"   ,  "GM.High"   ,  "GM.Low"   ,   "GM.Close"  ,  "GM.Volume", "GM.Adjusted")

TSLA1 <- as.xts(`TSLA`)
names(AAPL) <- c("TSLA.Open"   ,  "TSLA.High"   ,  "TSLA.Low"   ,   "TSLA.Close"  ,  "TSLA.Volume", "TSLA.Adjusted")

MSFT1 <- as.xts(`MSFT`)
names(AAPL) <- c("MSFT.Open"   ,  "MSFT.High"   ,  "MSFT.Low"   ,   "MSFT.Close"  ,  "MSFT.Volume", "MSFT.Adjusted")

NVDA1 <- as.xts(`NVDA`)
names(AAPL) <- c("NVDA.Open"   ,  "NVDA.High"   ,  "NVDA.Low"   ,   "NVDA.Close"  ,  "NVDA.Volume", "NVDA.Adjusted")

COST1 <- as.xts(`COST`)
names(COST) <- c("COST.Open"   ,  "COST.High"   ,  "COST.Low"   ,   "COST.Close"  ,  "COST.Volume", "COST.Adjusted")
```

```{r}
lineChart(AAPL1, line.type = 'h', subset = '2019-01::', theme = chartTheme('white'), up.col = '#60BD68')
```

The plot above is a static cumulative market value plot for Apple. The plot includes price data from 2019-01-01 to 2021-12. At the bottom of the plot, the trading volume of the stock for each recorded trading days are demonstrated in the form of histogram. No clear type of distribution of the volume can be easily identified due to the volatile nature of the stock market. Possible inflex and efflux might be found near the day when Apple announces its quarterly sales report or the day when a new Iphone product goes public. 

```{r}
lineChart(GM1, line.type = 'h', subset = '2019-01::', theme = chartTheme('white'), up.col = '#60BD68')
```

The plot above is a static cumulative market value plot for General Motor. The plot includes price data from 2019-01 to 2021-12. At the bottom of the plot, the trading volume of the stock for each recorded trading days are demonstrated in the form of histogram. No clear type of distribution of the volume can be easily identified due to the volatile nature of the stock market. Possible inflex and efflux might be found near the day when General Motor announces its quarterly sales report. The inflation might also have an effect on the stock price of GM if the price of the raw material go up.


```{r}
lineChart(TSLA1, line.type = 'h', subset = '2019-01::', theme = chartTheme('white'), up.col = '#60BD68')
```

The plot above is a static cumulative market value plot for Tesla. The plot includes price data from 2019-01 to 2021-12. At the bottom of the plot, the trading volume of the stock for each recorded trading days are demonstrated in the form of histogram. No clear type of distribution of the volume can be easily identified due to the volatile nature of the stock market. Possible inflex and efflux might be found near the day when Tesla announces its quarterly sales report. Price could also change rapidly if a new Tesla model is published. The direction of the price changes might depend on the performance of the Tesla Press Conference. Tweets sent by Elon Musk might also have some effects on the stock prices. 

```{r}
lineChart(MSFT1, line.type = 'h', subset = '2019-01::', theme = chartTheme('white'), up.col = '#60BD68')
```

The plot above is a static cumulative market value plot for Microsoft. The plot includes price data from 2019-01 to 2021-12. At the bottom of the plot, the trading volume of the stock for each recorded trading days are demonstrated in the form of histogram. No clear type of distribution of the volume can be easily identified due to the volatile nature of the stock market. Possible inflex and efflux might be found near the day when Microsoft announces its quarterly sales report. Insider trading that traced back to high executives in Microsoft and alleged or verified scandal of key officials of the Microsoft could exert negative influence on the stock prices.


```{r}
lineChart(COST1, line.type = 'h', subset = '2019-01::',theme = chartTheme('white'), up.col = '#60BD68')
```

The plot above is a static cumulative market value plot for Costco. The plot includes price data from 2019-01 to 2021-12. At the bottom of the plot, the trading volume of the stock for each recorded trading days are demonstrated in the form of histogram. No clear type of distribution of the volume can be easily identified due to the volatile nature of the stock market. Possible inflex and efflux might be found near the day when Costco announces its quarterly sales report. Inflation could exert significant influence on the stock prices as the rise of price of commodities would push up the total sales figure of the products.


```{r}
lineChart(NVDA1, line.type = 'h', subset = '2019-01::', theme = chartTheme('white'), up.col = '#60BD68')
```

The plot above is a static cumulative market value plot for Nvidia. The plot includes price data from 2019-01 to 2021-12. At the bottom of the plot, the trading volume of the stock for each recorded trading days are demonstrated in the form of histogram. No clear type of distribution of the volume can be easily identified due to the volatile nature of the stock market. Possible inflex and efflux might be found near the day when Nvidia announces its quarterly sales report. Tech trends such as Metaverse can positively influence the stock price of Nvidia as more buyers hold bullish views on the Tech company. Increasing demand for computational centers could also influence the stock price of Nvidia.   





```{r, include=FALSE}
aapl_gain = read.csv(file = 'final_data/aapl_gain.csv')
cost_gain = read.csv(file = 'final_data/cost_gain.csv')
msft_gain = read.csv(file = 'final_data/msft_gain.csv')
tsla_gain = read.csv(file = 'final_data/tsla_gain.csv')
nvda_gain = read.csv(file = 'final_data/nvda_gain.csv')
gm_gain = read.csv(file = 'final_data/gm_gain.csv')

```


```{r, include=FALSE}
aapl_gain$sym <- 'aapl'
cost_gain$sym <- 'cost'
msft_gain$sym <- 'msft'
tsla_gain$sym <- 'tsla'
nvda_gain$sym <- 'nvda'
gm_gain$sym <- 'gm'
```

```{r}
aapl_gain <- mutate(aapl_gain, color = ifelse(growth > 0, 1, 0))
cost_gain <- mutate(cost_gain, color = ifelse(growth > 0, 1, 0))
msft_gain <- mutate(msft_gain, color = ifelse(growth > 0, 1, 0))
tsla_gain <- mutate(tsla_gain, color = ifelse(growth > 0, 1, 0))
nvda_gain <- mutate(nvda_gain, color = ifelse(growth > 0, 1, 0))
gm_gain <- mutate(gm_gain, color = ifelse(growth > 0, 1, 0))
```



```{r}
ggplot(aapl_gain, aes(x=Date, y=growth, fill=color))+
  geom_col(position = "identity", colour = "black", size = 0.25)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

The plot above is a barchart demonstrating the growth rate of the investment in Apple using Golden Cross Method. Blue bar represents a positive growth while the black bar represents a decline. Within 17 trading days, the golden cross method achieves 9 growth increases. The size of most positive growth bar exceed the size of the negative ones.

```{r}
ggplot(nvda_gain, aes(x=Date, y=growth, fill=color))+
  geom_col(position = "identity", colour = "black", size = 0.25)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

The plot above is a barchart demonstrating the growth rate of the investment in Nvidia using Golden Cross Method. Blue bar represents a positive growth while the black bar represents a decline. Within 17 trading days, the golden cross method achieves 11 growth increases. The size of most positive growth bar exceed the size of the negative ones.

```{r}
ggplot(msft_gain, aes(x=Date, y=growth, fill=color))+
  geom_col(position = "identity", colour = "black", size = 0.25)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

The plot above is a barchart demonstrating the growth rate of the investment in Microsoft using Golden Cross Method. Blue bar represents a positive growth while the black bar represents a decline. Within 14 trading days, the golden cross method achieves 7 growth increases. The size of most positive growth bars exceed the size of the negative ones.

```{r}
ggplot(gm_gain, aes(x=Date, y=growth, fill=color))+
  geom_col(position = "identity", colour = "black", size = 0.25)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

The plot above is a barchart demonstrating the growth rate of the investment in General Motor using Golden Cross Method. Blue bar represents a positive growth while the black bar represents a decline. Within 17 trading days, the golden cross method achieves 7 growth increases. The size of most positive growth bars exceed the size of the negative ones.

```{r}
ggplot(cost_gain, aes(x=Date, y=growth, fill=color))+
  geom_col(position = "identity", colour = "black", size = 0.25)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

The plot above is a barchart demonstrating the growth rate of the investment in Costco using Golden Cross Method. Blue bar represents a positive growth while the black bar represents a decline. Within 17 trading days, the golden cross method achieves 9 growth increases. The size of most positive growth bars exceed the size of the negative ones.

```{r}
ggplot(tsla_gain, aes(x=Date, y=growth, fill=color))+
  geom_col(position = "identity", colour = "black", size = 0.25)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

The plot above is a barchart demonstrating the growth rate of the investment in Tesla using Golden Cross Method. Blue bar represents a positive growth while the black bar represents a decline. Within 17 trading days, the golden cross method achieves 8 growth increases. The size of most positive growth bars exceed the size of the negative ones.


```{r, include=FALSE}
df_stock <- rbind(aapl_gain, cost_gain ,msft_gain, tsla_gain,nvda_gain,gm_gain )
```


```{r}
df_stock_value <- na.omit(df_stock)
```


```{r}
df_stock_value <- mutate(df_stock_value, Days_Movement = ifelse(growth > 0, 'rise', 'fall'))
df_stock_value <- mutate(df_stock_value, stats_num = ifelse(growth > 0, 1, 1))
df_stock_value <- mutate(df_stock_value, color = ifelse(growth > 0, 1, 0))
```


```{r}


stockcolors <- c("#F15854","#60BD68")
counts <- df_stock_value %>%
  group_by(sym, Days_Movement) %>%
  summarize(Freq = sum(stats_num))

vcd::mosaic(Days_Movement_sym, direction = c("v", "h"), counts,highlighting_fill=stockcolors,
            main = "Investment Growth Movement on various trading days")

```

The plot above is a mosaic plot demonstrating the Investment Growth Movement on Various trading days. We can see that NVDA has the largest proportion of the trading days where the Golden Cross investment method produces a positive growth rate. Meanwhile, GM has the largest proportion of the trading days where the Golden Cross investment method produces a negative growth rate.



```{r}

cbbPalette <- c("#F15854","#60BD68")
tb3color <- scale_fill_manual(values=c(cbbPalette))
bp<- ggplot(df_stock_value, aes(x="", y=growth, fill=Days_Movement))+
geom_bar(width = 1, stat = "identity")+tb3color
pie <- bp + coord_polar("y", start=0)
pie
```
The piechart above shows that the Golden Cross method produces a positive growth rates roughly 1/9 of the total number of trading attempts. A trading attempt occur when a pair of adjacent buy and sell signals are produces by Golden Cross method. We can also concluded that the Golden Cross investing method has a 11% achieving positive growth on the selected stocks.



```{r}
df_stock['Close']
```


```{r}

ggplot(df_stock, aes(x = Close, y = sym, fill = sym)) +
  geom_density_ridges() +
  theme_ridges() + 
  theme(legend.position = "none")
```
The ridge plot above demonstrates the distribution of Closing prices for each selected stock over years (2019 to 2021). As expected, the distribution of TSLA is multimodal due to the high volatility of the stock prices of TSLA. The distribution of the closing prices for the other stocks resemble the normal distribution. Apple has a set of overall higher closing prices comparing to the others while GM has an overall lower closing prices comparing to the other stocks.


```{r}
chartSeries(AAPL1, 
            type = c("auto", "candlestick"), 
            subset = '2019-01::',
            show.grid = TRUE,
            theme='white',
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addSMA(n=10,col = 'blue'),addSMA(n=20,col = 'white')))
```

The plot above is a static candlestick plot demonstrating the price movement of Apple with Moving Average lines and Moving Average Convergence Divergence indicator (MACD). The plot includes price data from 2019-01 to 2021-12. The Convergence and Divergence of the short term moving average and long term moving average can be visualized by the MACD indicator, which is useful for the execution of Golden Cross method.



```{r}

chartSeries(NVDA1, 
            type = c("auto", "candlestick"), 
            subset = '2019-01::',
            show.grid = TRUE,
            theme='white',
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addSMA(n=10,col = 'blue'),addSMA(n=20,col = 'white')))
```

The plot above is a static candlestick plot demonstrating the price movement of NVDA with Moving Average lines and Moving Average Convergence Divergence indicator (MACD). The plot includes price data from 2019-01 to 2021-12. The Convergence and Divergence of the short term moving average and long term moving average can be visualized by the MACD indicator, which is useful for the execution of Golden Cross method.


```{r}
chartSeries(GM1, 
            type = c("auto", "candlestick"), 
            subset = '2019-01::',
            show.grid = TRUE,
            theme='white',
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addSMA(n=10,col = 'blue'),addSMA(n=20,col = 'white')))
```


The plot above is a static candlestick plot demonstrating the price movement of GM with Moving Average lines and Moving Average Convergence Divergence indicator (MACD). The plot includes price data from 2019-01 to 2021-12. The Convergence and Divergence of the short term moving average and long term moving average can be visualized by the MACD indicator, which is useful for the execution of Golden Cross method.

```{r}
chartSeries(COST1, 
            type = c("auto", "candlestick"), 
            subset = '2019-01::',
            show.grid = TRUE,
            theme='white',
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addSMA(n=10,col = 'blue'),addSMA(n=20,col = 'white')))
```


The plot above is a static candlestick plot demonstrating the price movement of COST with Moving Average lines and Moving Average Convergence Divergence indicator (MACD). The plot includes price data from 2019-01 to 2021-12. The Convergence and Divergence of the short term moving average and long term moving average can be visualized by the MACD indicator, which is useful for the execution of Golden Cross method.

```{r}
chartSeries(MSFT1, 
            type = c("auto", "candlestick"), 
            subset = '2019-01::',
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            theme='white',
            multi.col = FALSE,
            TA=c(addMACD(),addSMA(n=10,col = 'blue'),addSMA(n=20,col = 'white')))
```


The plot above is a static candlestick plot demonstrating the price movement of MSFT with Moving Average lines and Moving Average Convergence Divergence indicator (MACD). The plot includes price data from 2019-01 to 2021-12. The Convergence and Divergence of the short term moving average and long term moving average can be visualized by the MACD indicator, which is useful for the execution of Golden Cross method.

```{r}
chartSeries(TSLA1, 
            type = c("auto", "candlestick"), 
            subset = '2019-01::',
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            theme='white',
            multi.col = FALSE,
            TA=c(addMACD(),addSMA(n=10,col = 'blue'),addSMA(n=20,col = 'white')))
```


The plot above is a static candlestick plot demonstrating the price movement of TSLA with Moving Average lines and Moving Average Convergence Divergence indicator (MACD). The plot includes price data from 2019-01 to 2021-12. The Convergence and Divergence of the short term moving average and long term moving average can be visualized by the MACD indicator, which is useful for the execution of Golden Cross method.

Golden Cross Investment Return:

```{r}
ggplot(df_stock, aes(x=Date, y=X10000, group=sym, color = sym))+
  geom_line(aes(group=sym))+
  geom_point() +
  xlab('Trading Days')+
  ylab('Investment Returns ($)')+
  labs(title="Golden Cross Investment Returns Over time (Start from $10000)")+
  scale_x_discrete(guide = guide_axis(n.dodge=2))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.1, hjust=1))


```


The plot above is a line plot demonstrating the investment returns for different stocks using Golden Cross Method. The initial investment is $10000 for each stocks and we only buy the stock when a buy signal is created. We sell only when a sell signal is created. Buy and sell signals are created based on the following rules: if the short-term moving average line crosses the long-term moving average line from below, a buy signal is created. When the short-term moving average line crosses the long-term moving average line from above, a sell signal is created.

As shown in the plot, TSLA gives the greatest return while GM gives the least return. The volatility of TSLA is also much greater than the other stocks in the plot, as TSLA experiences rapid growth over the years. 




```{r}
ggplot(df_stock, aes(x=reorder(sym,growth, median, na.rm = TRUE), y=growth, color=sym)) + 
  geom_boxplot() + coord_flip() +
  xlab('Stock')+
  ylab('Investment Growth Over Time')+
  labs(title="Golden Cross Investment Returns Over time")
```
The above is a boxplot demonstrating the Golden Cross investment growth rates over the span of trading days. All the boxes are arranged by median in decreasing order. We can see that Nvidia has the highest median growth rates while the General Motor has the lowest growth rate, which explained the reason that the investment in General Motor increase the least in previous plot. TSLA has the most extreme outlier compared to all the other stocks, which accounts for the volatile investment return of TSLA in the previous plot.



```{r}
compond_rate = c(tail(aapl_gain$rate, n=1),
                 tail(cost_gain$rate, n=1),
                 tail(msft_gain$rate, n=1),
                 tail(tsla_gain$rate, n=1),
                 tail(nvda_gain$rate, n=1),
                 tail(gm_gain$rate, n=1))

df_compond <- data.frame(compond_rate)

ggplot(df_compond, aes(y= df_compond$compond_rate)) + 
  geom_boxplot()+
  geom_hline(yintercept=0.8294, linetype="dashed", color = "red", size=1)+
  annotate(geom="text", x=0, y=-1, label="82.94% average S&P 500 return from 2019 to 2021",
              color="red")+
  ylab('Investment Compond Growth rate')+
  labs(title="Golden Cross Investment Componded Return Rate (All the stock combined)")

```

```{r, include=FALSE}
df_compond$compond_rate
```
The plot above is a boxplot demonstrating the Golden Cross Investment Componded Return Rate for all the stocks. The red horizontal dash line represent the average S&P 500 growth from 2019 to 2021. The data of the actual return of S&P 500 over years comes from online Stock Broker. The lowest growth rate is 65% while the highest growth rate is 1826%. The median growth rate is slightly higher than the average growth rate of S&P 500 index funds. Since conventionally the S&P 500 index funds represent the performance of the general stock market, we can see that Golden Cross investment method outperform the general market returns when applied on the selected major stocks. 

<!--chapter:end:05-results.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Interactive component

Package 'plotly' and 'quantmod' are necessary for interactive Candlestick visualization. 

```{r, include=FALSE}
library(plotly)
library(quantmod)
library(ggplot2)
library(dplyr)
```

Interactive:

```{r, include=FALSE}

AAPL <- read.csv(file = 'final_data/AAPL.csv')

fig_aapl <- AAPL %>% plot_ly(x = AAPL$Date, type="candlestick",
          open = AAPL$Open, close = AAPL$Close,
          high = AAPL$High, low = AAPL$Low, showlegend = FALSE)

fig_aapl <- fig_aapl %>% layout(title = "AAPL Candlestick Chart",
         xaxis = list(rangeslider = list(visible = F)),  yaxis = list(title = 'Price ($)'))


fig_aapl <- fig_aapl %>% add_lines(x = ~Date, y = ~Open_10 , name = "10 MA",
            line = list(color = 'blue', width = 1.5),
            legendgroup = "10 MA",
            hoverinfo = "none", inherit = F) 


fig_aapl <- fig_aapl %>% add_lines(x = ~Date, y = ~Open_20, name = "20 MA",
            line = list(color =  'purple', width = 1.5),
            legendgroup = "20 MA", inherit = F, hoverinfo = "none") 


```

```{r}
fig_aapl
```

The plot above is an interactive candlestick plot demonstrating the price movement of Apple. The plot includes price data from 2019-01-30 to 2021-10-21. Aside from the candle sticks, the 10-day moving average and the 20-day moving average are also displayed. These two moving average lines form vital indicators for the Golden Cross Investing method.

```{r, include=FALSE}

COST <- read.csv(file = 'final_data/COST.csv')

fig_cost <- COST %>% plot_ly(x = AAPL$Date, type="candlestick",
          open = COST$Open, close = COST$Close,
          high = COST$High, low = COST$Low, showlegend = FALSE)

fig_cost <- fig_cost %>% layout(title = "COST Candlestick Chart",
         xaxis = list(rangeslider = list(visible = F)),  yaxis = list(title = 'Price ($)'))


fig_cost <- fig_cost %>% add_lines(x = ~Date, y = ~Open_10 , name = "10 MA",
            line = list(color = 'blue', width = 1.5),
            legendgroup = "10 MA",
            hoverinfo = "none", inherit = F) 


fig_cost <- fig_cost %>% add_lines(x = ~Date, y = ~Open_20, name = "20 MA",
            line = list(color =  'purple', width = 1.5),
            legendgroup = "20 MA", inherit = F, hoverinfo = "none") 



```

```{r}
fig_cost
```

The plot above is an interactive candlestick plot demonstrating the price movement of Costco. The plot includes price data from 2019-01-30 to 2021-10-21. Aside from the candle sticks, the 10-day moving average and the 20-day moving average are also displayed. These two moving average lines form vital indicators for the Golden Cross Investing method.


```{r, include=FALSE}
MSFT <- read.csv(file = 'final_data/MSFT.csv')

fig_msft <- MSFT %>% plot_ly(x = MSFT$Date, type="candlestick",
          open = MSFT$Open, close = MSFT$Close,
          high = MSFT$High, low = MSFT$Low, showlegend = FALSE)

fig_msft <- fig_msft %>% layout(title = "MSFT Candlestick Chart",
         xaxis = list(rangeslider = list(visible = F)),  yaxis = list(title = 'Price ($)'))


fig_msft <- fig_msft %>% add_lines(x = ~Date, y = ~Open_10 , name = "10 MA",
            line = list(color = 'blue', width = 1.5),
            legendgroup = "10 MA",
            hoverinfo = "none", inherit = F) 


fig_msft <- fig_msft%>% add_lines(x = ~Date, y = ~Open_20, name = "20 MA",
            line = list(color =  'purple', width = 1.5),
            legendgroup = "20 MA", inherit = F, hoverinfo = "none") 



```

```{r}
fig_msft
```

The plot above is an interactive candlestick plot demonstrating the price movement of Microsoft. The plot includes price data from 2019-01-30 to 2021-10-21. Aside from the candle sticks, the 10-day moving average and the 20-day moving average are also displayed. These two moving average lines form vital indicators for the Golden Cross Investing method.

```{r, include=FALSE}
GM <- read.csv(file = 'final_data/GM.csv')

fig_gm <- GM %>% plot_ly(x = GM$Date, type="candlestick",
          open = GM$Open, close = GM$Close,
          high = GM$High, low = GM$Low, showlegend = FALSE)

fig_gm <- fig_gm %>% layout(title = "GM Candlestick Chart",
         xaxis = list(rangeslider = list(visible = F)),  yaxis = list(title = 'Price ($)'))


fig_gm <- fig_gm %>% add_lines(x = ~Date, y = ~Open_10 , name = "10 MA",
            line = list(color = 'blue', width = 1.5),
            legendgroup = "10 MA",
            hoverinfo = "none", inherit = F) 


fig_gm <- fig_gm %>% add_lines(x = ~Date, y = ~Open_20, name = "20 MA",
            line = list(color =  'purple', width = 1.5),
            legendgroup = "20 MA", inherit = F, hoverinfo = "none") 



```

```{r}
fig_gm
```

The plot above is an interactive candlestick plot demonstrating the price movement of General Motor. The plot includes price data from 2019-01-30 to 2021-10-21. Aside from the candle sticks, the 10-day moving average and the 20-day moving average are also displayed. These two moving average lines form vital indicators for the Golden Cross Investing method. Notice that during the pandamic lockdown, the price of GM decreased significantly. This drasitic decrease could be related to the shutdown of global production lines and travel restrictions.

```{r, include=FALSE}
NVDA <- read.csv(file = 'final_data/NVDA.csv')

fig_nvda <- NVDA %>% plot_ly(x = NVDA$Date, type="candlestick",
          open = NVDA$Open, close = NVDA$Close,
          high = NVDA$High, low = NVDA$Low, showlegend = FALSE)

fig_nvda <- fig_nvda %>% layout(title = "NVDA Candlestick Chart",
         xaxis = list(rangeslider = list(visible = F)),  yaxis = list(title = 'Price ($)'))


fig_nvda <- fig_nvda %>% add_lines(x = ~Date, y = ~Open_10 , name = "10 MA",
            line = list(color = 'blue', width = 1.5),
            legendgroup = "10 MA",
            hoverinfo = "none", inherit = F) 


fig_nvda <- fig_nvda %>% add_lines(x = ~Date, y = ~Open_20, name = "20 MA",
            line = list(color =  'purple', width = 1.5),
            legendgroup = "20 MA", inherit = F, hoverinfo = "none") 



```

```{r}
fig_nvda
```

The plot above is an interactive candlestick plot demonstrating the price movement of Nvida. The plot includes price data from 2019-01-30 to 2021-10-21. Aside from the candle sticks, the 10-day moving average and the 20-day moving average are also displayed. These two moving average lines form vital indicators for the Golden Cross Investing method.

```{r, include=FALSE}
TSLA <- read.csv(file = 'final_data/TSLA.csv')

fig_tsla <- TSLA %>% plot_ly(x = TSLA$Date, type="candlestick",
          open = TSLA$Open, close = TSLA$Close,
          high = TSLA$High, low = TSLA$Low, showlegend = FALSE)

fig_tsla <- fig_tsla%>% layout(title = "TSLA Candlestick Chart",
         xaxis = list(rangeslider = list(visible = F)),  yaxis = list(title = 'Price ($)'))


fig_tsla <- fig_tsla %>% add_lines(x = ~Date, y = ~Open_10 , name = "10 MA",
            line = list(color = 'blue', width = 1.5),
            legendgroup = "10 MA",
            hoverinfo = "none", inherit = F) 


fig_tsla <- fig_tsla %>% add_lines(x = ~Date, y = ~Open_20, name = "20 MA",
            line = list(color =  'purple', width = 1.5),
            legendgroup = "20 MA", inherit = F, hoverinfo = "none") 


```

```{r}
fig_tsla
```

The plot above is an interactive candlestick plot demonstrating the price movement of Tesla. The plot includes price data from 2019-01-30 to 2021-10-21. Aside from the candle sticks, the 10-day moving average and the 20-day moving average are also displayed. These two moving average lines form vital indicators for the Golden Cross Investing method.


```{r, include=FALSE}
library(grid)
library(gridExtra)
```

```{r}
fig <- subplot(fig_aapl, fig_cost, fig_msft, fig_tsla, fig_nvda, fig_gm,  nrows=2)  %>%
  layout(title = list(text = "Stock Price with Moving Average"),
         plot_bgcolor='#e5ecf6', 
         xaxis = list( 
           zerolinecolor = '#ffff', 
           zerolinewidth = 2, 
           gridcolor = 'ffff'), 
         yaxis = list( 
           zerolinecolor = '#ffff', 
           zerolinewidth = 2, 
           gridcolor = 'ffff'))
fig
```

The plot above is a combination of all the interactive candlestick plots for six different major stocks traded in the U.S. stock exchange.The plot includes price data from 2019-01-30 to 2021-10-21. 10-day moving average line and 20-day moving average line are plotted on top of each candlestick plot.

<!--chapter:end:06-interactive.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Conclusion

<!--chapter:end:07-conclusion.Rmd-->

